\documentclass[11pt]{letter}

\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{setspace}
\usepackage{hyperref}

\signature{Javier Macias-Guarasa\\Universidad de Alcalá\\\texttt{javier.maciasguarasa@uah.es}}

\begin{document}

\begin{letter}{Editors of \textit{Scientific Data}}

\opening{Dear Editors,}

We are pleased to submit our manuscript entitled \textbf{``A distributed acoustic sensing dataset for vessel detection and localization in submarine cable protection tasks''} to be considered for publication the \textit{Scientific Data} Journal. The submission includes a curated submarine DAS dataset to be used in submarine cable protection applications, together with the associated processing scripts, provided in accordance with the journal's data-transparency requirements.

In line with the journal’s guidance for covering letters, we note the following:

\begin{itemize}
    \item We have no suggested or non-preferred reviewers beyond standard conflict-of-interest criteria handled by the submission system.
    \item All related prior publications have been disclosed through the submission portal.
    \item Authorship, affiliations, and contributions have been entered as required.
\end{itemize}

We confirm that the manuscript is original, has not been published previously, and is not under consideration elsewhere. All authors approve the submitted version.

Thank you for your consideration.

\closing{Sincerely,\\[1.5ex]On behalf of all authors,}

\end{letter}

\end{document}

